Multi sky-view\\ 3D aerosol distribution recovery

### 2013-10-14 article.tex
Yoav last changes

\Cref{fig:cross_sections} plots the intensity profile
along a horizontal cross section of the viewed field,
comparing photographs simulated using the single-scattering and the  MC forward models.
\Cref{fig:cross_sections}(a) is extracted from \cref{fig:simulation-results1}(d)
and \cref{fig:simulation_particles}(a) of the {\em Haze Blobs} scene.
This plot demonstrates consistency in this scene, for most pixels.
\Cref{fig:cross_sections}(b) plots the same profiles,
where the aerosol density was increased tenfold (see \cref{sec:optimization-results}
and the corresponding MC photograph, \cref{fig:simulation_particles}(d)).
In \cref{fig:cross_sections}(b) the plots differ more than in \cref{fig:cross_sections}(a),
due to high order scattering.
\begin{figure}[t]
  \centering
  \yoavcomment{\includegraphics{images/cross_sections.pdf}}
  \caption{\small Cross-sections along the $X$-axis of photographs rendered
    by the single-scattering (dotted) and MC (solid line) forward models.
    (a) cross sections of the {\em Haze Blobs} scene (described in \cref{sec:simul}).
    The difference between the models is much more pronounced (b) 
    when the scatterers are ten times denser (see \cref{sec:optimization-results}).
  }
  \label{fig:cross_sections}
\end{figure}

>>>>

\Cref{fig:cross_sections} plots the image intensity profile along a straight
line from left to right, via the image center (zenith). The plot compares
photographs simulated using the single-scattering and the  MC forward models.
\Cref{fig:cross_sections}(a) is extracted from \cref{fig:simulation-results1}(d)
and \cref{fig:simulation_particles}(a) of the {\em Haze Blobs} scene.
This plot demonstrates consistency in this scene, for most pixels.
\Cref{fig:cross_sections}(b) plots the same profiles,
where the aerosol density was increased tenfold (see \cref{sec:optimization-results}
and the corresponding MC photograph, \cref{fig:simulation_particles}(d)).
In \cref{fig:cross_sections}(b) the plots differ more than in \cref{fig:cross_sections}(a),
due to high order scattering.
\begin{figure}[t]
  \centering
  \yoavcomment{\includegraphics{images/cross_sections.pdf}}
  \caption{\small Cross-sections along the $X$-axis of photographs rendered
    by the single-scattering (dotted) and MC (solid line) forward models.
    (a) cross sections of the {\em Haze Blobs} scene (described in \cref{sec:simul}).
    The difference between the models is much more pronounced (b) 
    when the scatterers are ten times denser (see \cref{sec:optimization-results}).
  }
  \label{fig:cross_sections}
\end{figure}
